Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-18 paper/ijcai/paper.tex
note
small fix

\begin{abstract}
  Software debugging is difficult. One of its main challenges is the improvement of Spectrum-based Fault Localization (SBFL) scores accuracy. We suspect that several highly ranked statements - covered by failing executions - may be unrelated to the fault. This paper reports the results of a comprehensive study perfomed to reassess the impact of combining Dynamic Slicing with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL. We leverage the Mozzila's Lithium Slicer engine to minimize the top-5 and top-10 classes that comprise the highest scored faulty statements of the Defects4j failing tests. The SFL score is computed before and after applying DS to calculate the impact of Tandem-FL.
  Our results show that adding DS to SFL improves the diagnosis accuracy of SFL. 
\end{abstract}

@@

The oracle idea is based on the statement deletion mutant operator. This operator was designed based on 
the idea that each statement has an effect on the test output (i.e., oracle).

>>>>

\begin{abstract}
  Software debugging is difficult. One of its main challenges is the improvement of Spectrum-based Fault Localization (SBFL) scores accuracy. We suspect that several highly ranked statements - covered by failing executions - may be unrelated to the fault. This paper reports the results of a comprehensive study perfomed to reassess the impact of combining Dynamic Slicing with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL. We leverage the Mozzila's Lithium Slicer engine to minimize the top-5 and top-10 classes that comprise the highest scored faulty statements of the Defects4j failing tests. The SFL score is computed before and after applying DS to calculate the impact of Tandem-FL.
  Our results show that adding DS to SFL improves its diagnosis accuracy. 
\end{abstract}

@@

\Sof{Not finished yet}The oracle idea is based on the statement deletion mutant operator. This operator was designed based on 
the idea that each statement has an effect on the test output (i.e., oracle).
